Bridging the Gap Between Visual and Analytical Machine Learning Testing

### 2023-09-19 report/esecfse24.tex
feat(report): init methodology figures

\begin{table}
  \centering
  \caption{Observations from random samples of notebooks with various
  cell arrangement.}
  \begin{tabular}{p{0.4\textwidth} p{0.4\textwidth}}
    \toprule
    \emph{\textbf{Cell arrangement}} &
    \emph{\textbf{Observations}}\\
    \midrule
    Assertion above visualisation cell &
    The assertions in this arrangement were typically not related to
    the visualisation below. Often, a markdown cell present between
    the assertion and visualisation code cells, would mark the
    begining of a new section in the notebook. In other cases, the
    assertions were typically pre-condition checks to ensure that the
    visualisation code would not encounter any errors.\\
    \bottomrule
  \end{tabular}
  \label{tab:cell-arrangement}
\end{table}

>>>>

\begin{table}
  \centering
  \caption{Observations from random samples of notebooks with various
  cell arrangement.}
  \begin{tabular}{p{0.4\textwidth} p{0.4\textwidth}}
    \toprule
    \emph{\textbf{Cell arrangement}} &
    \emph{\textbf{Observations}}\\
    \midrule
    Assertion above visualisation cell &
    The assertions in this arrangement were typically not related to the visualisation below. Often, a markdown cell present between the assertion and visualisation code cells, would mark the begining of a new section in the notebook. In other cases, the assertions were typically pre-condition checks to ensure that the visualisation code would not encounter any errors. Pre-condition checks typically include checking the shape of features that are used in the visualisation. Or checking that the length of the ``x''and ``y`` features are the same to ensure a continuous line in the plot.\\
    Assertion in the visualisation cell &
    There are two possible scenarios here:
    \begin{enumerate}
    \item[2.1]{This is the first one.}
    \item[2.2]{This is the second one.}
    \end{enumerate}\\

    \bottomrule
  \end{tabular}
  \label{tab:cell-arrangement}
\end{table}
